Thesis outline

### 2017-07-20 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Fixed typo

In contrast, dwarf galaxies within 0.05 \hMpc of the center of the nearest group 
have lower oxygen (O/H) and nitrogen (N/H) abundances (O/H) than average.  Due 
to their proximity to the group center, it is likely that these dwarf galaxies 
are not able to retain as much of their heavy elements as a more isolated 
galaxy, thereby reducing their gas-phase oxygen and nitrogen abundances.

>>>>

In contrast, dwarf galaxies within 0.05 \hMpc of the center of the nearest group 
have lower oxygen (O/H) and nitrogen (N/H) abundances than average.  Due to 
their proximity to the group center, it is likely that these dwarf galaxies are 
not able to retain as much of their heavy elements as a more isolated galaxy, 
thereby reducing their gas-phase oxygen and nitrogen abundances.
